---
title: "HW5"
author: "Ruwen Zhou"
date: "11/18/2020"
output:
  pdf_document: default
  github_document: default
---

```{r setup, include = FALSE}
library(tidyverse)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 1

Read in the data.

```{r}
homicide_df = 
  read_csv("homicide_data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")
```


Let's look at this a bit

```{r}
aggregate_df = 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )
```

Can I do a prop test for a single city?

```{r}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved), 
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)) %>% 
  broom::tidy()
```

Try to iterate ........

```{r}
results_df = 
  aggregate_df %>% 
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)
```



```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```



```{r, error = TRUE}

homicide_df = 
  read_csv("homicide_data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL") %>% 
  nest(data = resolved)
```

## Problem 2

### Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time
```{r}
tidy_df = tibble(
    path = list.files("lda_data"),
  ) %>% 
  mutate(
    path = str_c("lda_data/", path),
    data = map(.x = path, ~read_csv(.x)),
    arm_id = str_remove(path, "lda_data/"),
    arm_id = str_remove(arm_id, ".csv")) %>% 
  unnest(data) %>% 
  select(-path) %>% 
  pivot_longer(
    week_1:week_8,
    values_to = "observation_data",
    names_to = "week",
    names_prefix = "week_",
  ) %>% 
  separate(arm_id, into = c("arm", "subject_id"), sep = "_")
tidy_df %>% knitr::kable()
tidy_df
```

### Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups
```{r}
tidy_df %>%
  unite("arm_id", c(arm, subject_id), sep = "_", remove = F) %>%
  ggplot(aes(x = week, y = observation_data)) +
  geom_path(aes(color = arm, group = as.factor(arm_id)),alpha = 0.5) +
  labs(
    x = "Week",
    y = "Observation value",
    title = "Observations on each subject among two arms wihtin 8 weeks"
    )
```
The observation data of experimental arm increases faster than the control arm over time. The measure in control arm is more stable and decreases a little bit after week 6.

## Problem 3

### T test
```{r}
n = 30
mu = 0
sigma = 5
x = rnorm(n, mean = mu, sd = sigma)
t.test(x, mu = mu, conf.level = 0.95)
```
### Generate 5000 datasets from the model
```{r}
sim_data = function(n = 30, mu = 0, sigma = 5) {
     x = rnorm(n, mean = mu, sd = sigma)
     t_test = t.test(x, conf.int = 0.95) %>% broom::tidy()
     t_test
}
output = vector("list", 5000)
for (i in 1:5000) {
  output[[i]] = sim_data()
}
output %>% head()

```
### for mu = {0,1,2,3,4,5,6}
```{r}
set.seed(1000)
combine = 
  tibble(mu = c(0, 1, 2, 3, 4, 5, 6)) %>% 
  mutate(
    output = map(.x = mu, ~rerun(5000, sim_data(mu = .x))),
    new = map(output, bind_rows)) %>% 
  select(-output) %>% 
  unnest(new)
combine %>% head()
```

### Make a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of mu on the x axis. 

```{r}
combine %>% 
  filter(p.value < 0.05) %>% 
  group_by(mu) %>% 
  summarize(prop_rej = n()) %>% 
  mutate(prop_rej = prop_rej/5000) %>% 
  ggplot(aes(x = mu, y = prop_rej), color = mu) +
  geom_point() +
  geom_line() +
  scale_x_continuous(limits = c(0,6), breaks = seq(0,6,1)) +
  labs(
    title = "Power of the test over different mu",
    x = "The true value of mu",
    y = "Power of the test"
  )
```
As the number of mu increases, the power of the test also increases. The power converges to 1 when mu = 4.











